---
title: "Amirvahab Fakhfouri"
output: html_document
---

For this final, first of all, I made a database and define defferent tables on that.

```{r include=FALSE} 
library("dplyr")  #for dplyr
library("RSQLite") #for sqllite
library("nycflights13") #for data
library("ggplot2")
my_db <- src_sqlite("my_db.sqlite35", create = T)
flights_sqlite <- copy_to(
  my_db, flights, temporary = FALSE, 
  indexes = list(
    c("year", "month", "day"), 
    "carrier", 
    "tailnum")
)

airlines_sqlite <- copy_to(
  my_db, airlines, temporary = FALSE, 
  indexes = list("carrier")
)

airports_sqlite <- copy_to(
  my_db, airports, temporary = FALSE, 
  indexes = list("faa")
)

planes_sqlite <- copy_to(
  my_db, planes, temporary = FALSE, 
  indexes = list("tailnum")
)

weather_sqlite <- copy_to(
  my_db, weather, temporary = FALSE, 
  indexes = list(
    c("year", "month","day","hour"),
    "origin")
)
nycflights13_sqlite()
my_db
flights_sqlite <- tbl(my_db, "flights")
airliness_sqlite <- tbl(my_db, "airlines")
airports_sqlite <- tbl(my_db, "airports")
planes_sqlite <- tbl(my_db, "planes")
weather_sqlite <- tbl(my_db, "weather")


```

In this part, for the relationship between departure delay and weather,firstly, I am going to merge flights dataset and weather datasets as well as making a simple regression to investigate of impact of weather on departure delay.
```{r echo=T} 

flights_weather <- inner_join (
  tbl(my_db, "flights"),
  tbl(my_db, "weather"),
  by = c("year","month","day","hour")) %>%
  collect() 

D1<-(lm(flights_weather$dep_delay~flights_weather$temp+
             flights_weather$dewp+flights_weather$humid+
             flights_weather$wind_speed+flights_weather$pressure))
summary(D1)

```

Based on the above table results we can say that all of the weather variables are statistically significant. So based on the coefficient we can say each unit increase in each weather variable may increase/decrease dep delay by its coefficient.
```{r echo=T}
D2<-(lm(flights$dep_delay~flights$year+ flights$month+
           flights$day+flights$hour))
summary(D2)            
             
```

Based on the above table which is the relationship between departure delay and time variables, we can say that just month and hour are statistically significant. So it does not depend on the day.

```{r echo=T}
flights_airports<- inner_join (
  tbl(my_db, "flights"),
  tbl(my_db, "airports"),
  by = c("dest" = "faa")) %>%
  collect() 

D3<-(lm(flights_airports$dep_delay~flights_airports$lat+
             flights_airports$lon+flights_airports$alt))
summary(D3)
```

Based on the above table which is the relationship between departure delay and different airports, we can say that each direction of airports are statistically significant.

```{r echo=T}
flights_planes <- inner_join (
  tbl(my_db, "flights"),
  tbl(my_db, "planes"),
  by = "tailnum") %>%
  collect() 
D4<- (lm(flights_planes$dep_delay~
             flights_planes$engines+flights_planes$engine))
    summary(D4)         
             
```

Above table which is the relationship between departure delay and characteristics of plane says that none of them are statistically significant.
```{r echo=T}
flights= tbl(my_db, "flights") %>% 
               collect() %>%
               mutate(canceled = is.na(arr_time))
              
             
canceled.weather<-flights  %>% 
  inner_join(weather)             

C1<-(glm(canceled.weather$canceled~canceled.weather$temp+
             canceled.weather$dewp+canceled.weather$humid+
             canceled.weather$wind_speed+canceled.weather$pressure,family="binomial"(link="logit")))
summary(C1)
```

This table is about the relationship between canceled flight and weather. Based on the table we can say that only pressure of the weather is statistically significant in cancelation of the flight.

```{r echo=T}
C2<-(glm(flights$canceled~flights$year+ flights$month+
             flights$day+flights$hour,family="binomial"(link="logit")))
summary(C2)
```

This table is about the relationship between cancled flights and time variables. Based on this table we can say that just hour is statistically significant in the cancelation of the flights. 

```{r}
canceled.airports<-flights  %>% 
  inner_join(airports,by=c("dest" = "faa"))

C3<-(glm(canceled.airports$canceled~canceled.airports$lat+
              canceled.airports$lon+canceled.airports$alt,family="binomial"(link="logit")))
summary(C3)
```

This table is about the relationship between the canceled flights and different airports. Based on this table we can say that latitude and longitude are statistically significant. 

```{r echo=T}
canceled.planes<-flights  %>% 
  inner_join(planes,"tailnum")

C4<-(glm(canceled.planes$canceled~
               canceled.planes$engines+canceled.planes$engine,family="binomial"(link="logit")))

summary(C4)
```

The last table is about the canceled flights and characteristics of the flights. Based on this table we can say that just engines and jet in the characteristic are statistically significant.
So we can conclude that in the following situation we have departure delay: based on the tables above we know that weather is really important. So changing in each elements of weather may increase or decrease the departure delay. In addition, month and hour influence on departure delay. The directions of airport affect on that and the characteristics of planes do not affect in this delay.
For cancelation we can say that, pressure of the air is really important. In addition, hour play an important role on the cancelation of flights and directions of the airport are really important but characteristic are not that much importaant on the cancelation of the flight.

